CRUSE to Safe Cycling in Ireland

### 2023-09-14 paper.qmd
Add limitations of PCT approach

@@

-   Limited coverage of modes beyond travel to work and school

-   ...

>>>>

- Limited coverage of trip purposes beyond travel to work and school
- Low resolution of data, with routes starting and ending in administrative zone centroids
- A web interface that was not user-friendly or intuitive

The CRUSE project addressed these limitations as outlined in this paper.

@@
